---
title: "lm_simple_tutorial"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{lm_simple_tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Linear Regression with `lm_simple`

The `easyLM` package provides a minimal implementation of linear regression using ordinary least squares.

In this vignette, we will:

1. Fit a linear regression using `lm_simple()`
2. Compare the results to base R’s `lm()`
3. Benchmark performance of the function

```{r}
library(easyLM)

# Simulate data
set.seed(123)
n <- 50
x <- rnorm(n, mean = 5, sd = 2)
y <- 2 + 3*x + rnorm(n, sd = 1)
data <- data.frame(x, y)

# Fit with lm_simple
fit_simple <- lm_simple(y ~ x, data = data)
fit_simple

# Fit with base lm
fit_lm <- lm(y ~ x, data = data)
summary(fit_lm)

# Compare coefficients
all.equal(fit_simple$coef, coef(fit_lm), tolerance = 1e-6)

# Benchmark
library(microbenchmark)
microbenchmark(
  lm_simple = lm_simple(y ~ x, data = data),
  lm_base   = lm(y ~ x, data = data),
  times = 200
)
```

# Conclusion

The `lm_simple` function closely matches R's built-in `lm()` and provides a transparent, educational implementation of ordinary least squares.

